Fitness Cost

### 2022-01-24 graphs_newt_snakes/fitness_cost.Rmd
I am currently running a very long simulation to to see what happens overtime. I have also added some new graphs to fitness cost by looking at how different fitness cost effects the phenotype of the population. Even when there are different cost values all of the simulation reach a point where the it equiliborates on the time scale of drift. I have also started two new rmarkdowns/ experiments. One is to compare different genetic architectures (which I just finished running on the cluster) and the other is to look at steady-state of my co-evo cost simulation. I look forward to the results

c(p) = (a/b)^2
c(3) = (a/b)^2
log(2) = (a/b)^2
b = 3/log(2) = 10

SO cost = (phenotype/10)^2

@@

>>>>

c(p) = (a/b)^2
c(3) = (a/b)^2
log(2) = (a/b)^2
b = 3/log(2) = 4.2

SO cost = (phenotype/4.2)^2

I used 10 instead of 4.2 (due to math errors).

@@

## An Equilibrium

Is there a point where the cost of a phenotype reaches a balance with selection pressure experienced by the population?

```{r, cost equlibrium}

file$newt_equl <- file$Newt_mean_Pheno/file$cost
file$snake_equl <- file$Snake_mean_Pheno/file$cost

e1 <- ggplot(file, aes(gen, newt_equl, col=factor(cost))) + geom_line()+ 
    ggtitle("Newt Mean Pheno/Cost by Gen", subtitle = "Different Cost") +
    xlab("Generations") + ylab("Phenotype/Cost")+
    theme_bw()

e2 <- ggplot(file, aes(gen, snake_equl, col=factor(cost))) + geom_line()+ 
    ggtitle("Snake Mean Pheno/Cost by Gen", subtitle = "Different Cost") +
    xlab("Generations") + ylab("Phenotype/Cost")+
    theme_bw()

grid.arrange(e1, e2, nrow=1)
```

```{r, population size equlibrium}

pop1 <- ggplot(file, aes(gen, Newt_pop_size, col=factor(cost))) + geom_line()+ 
    ggtitle("Newt Popsize by Gen", subtitle = "Different Cost") +
    xlab("Popsize") + ylab("Phenotype/Cost")+
    theme_bw()

pop2 <- ggplot(file, aes(gen, Snake_pop_size, col=factor(cost))) + geom_line()+ 
    ggtitle("Snake Popsize by Gen", subtitle = "Different Cost") +
    xlab("Popsize") + ylab("Phenotype/Cost")+
    theme_bw()

grid.arrange(pop1, pop2, nrow=1)
```
